---
title: "Stock assessment results archive (SARA)"
author: "Jim Ianelli "
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(scales)
```
This shows some rudimentary ways to access the stock assessment results archive.

## Installation Instructions
This function likely depends on R version >=4.0.

Ensure that the "devtools" package from CRAN is installed

    # Install and load devtools package
    install.packages("devtools")
    library("devtools")

Next, install the SARA package from this GitHub repository using a function in the "devtools" package.  This may require using the `INSTALL_opts` option depending upon your version of R:

    # Install package
    install_github("afsc-assessments/SARA", INSTALL_opts="--no-staged-install")
    # Load package
    library(SARA)



## Accessing some results
Invoking `SARA()` will filter through the individual assessment result files in 
the data-raw directory and create a number of dataframes.

`library(SARA)`
`SARA()`
`df<-tibble(left_join(mod_stats,sara_stock));names(df) <- tolower(names(df))`
`glimpse(df)`
`df |> filter(assessyear==2021) |> ggplot(aes(x=spawnbiomass,y=recruitment,label=fisheryyear)) + `
`  geom_point(size=.2) + geom_smooth() + theme_minimal() + facet_wrap(stock~region,scale="free")`

```{r,echo=FALSE}
```

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
