---
title: "Stock assessment results archive (SARA)"
author: "Jim Ianelli "
date: "`r Sys.Date()`"
output: 
  bookdown::html_document2:
    code_folding: hide
    fig_caption: yes
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 3
    toc_float: yes
editor_options: 
  markdown: 
    wrap: 72
---

```{css zoom-lib-src, echo = FALSE}
script src = "https://ajax.googleapis.com/ajax/libs/jquery/3.4.1/jquery.min.js"
```

```{js zoom-jquery, echo = FALSE}
 $(document).ready(function() {
    $('body').prepend('<div class=\"zoomDiv\"><img src=\"\" class=\"zoomImg\"></div>');
    // onClick function for all plots (img's)
    $('img:not(.zoomImg)').click(function() {
      $('.zoomImg').attr('src', $(this).attr('src')).css({width: '100%'});
      $('.zoomDiv').css({opacity: '1', width: 'auto', border: '1px solid white', borderRadius: '5px', position: 'fixed', top: '50%', left: '50%', marginRight: '-50%', transform: 'translate(-50%, -50%)', boxShadow: '0px 0px 50px #888888', zIndex: '50', overflow: 'auto', maxHeight: '100%'});
    });
    // onClick function for zoomImg
    $('img.zoomImg').click(function() {
      $('.zoomDiv').css({opacity: '0', width: '0%'}); 
    });
  });
```

```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir=here::here())
knitr::opts_chunk$set(warning=FALSE, message=FALSE, echo=FALSE, results=FALSE,fig.width=6, fig.height=5)


knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
library(tidyverse)
library(scales)
library(SARA)
```
# Stock Assessment Results Repository (SARA)

This is intended to show some rudimentary ways to access the stock assessment 
results archive.

## Installation Instructions
This function likely depends on R version >=4.0.

Ensure that the "devtools" package from CRAN is installed

    # Install and load devtools package
    install.packages("devtools")
    library("devtools")

Next, install the SARA package from this GitHub repository using a function in the "devtools" package.  This may require using the `INSTALL_opts` option depending upon your version of R:

    # Install package
    install_github("afsc-assessments/SARA", INSTALL_opts="--no-staged-install")
    # Load package
    library(SARA)



## Accessing some results
Invoking `SARA()` will filter through the individual assessment result files in 
the data-raw directory and create a number of dataframes.

`library(SARA)`

`SARA()`

`df<-tibble(left_join(mod_stats,sara_stock));names(df) <- tolower(names(df))`

`glimpse(df)`

`df |> filter(assessyear==2021) |> ggplot(aes(x=spawnbiomass,y=recruitment,label=fisheryyear)) + `

`  geom_point(size=.2) + geom_smooth() + theme_minimal() + facet_wrap(stock~region,scale="free")`

```{r,echo=FALSE,warning=FALSE,fig.width=11,fig.height=18}
SARA()
df<-tibble(left_join(mod_stats,sara_stock));
names(df) <- tolower(names(df))

df |> filter(assessyear>=2019) |> mutate(Assessed_Year=as.factor(assessyear),
                                         Year=fisheryyear,SSB=spawnbiomass) |>
  ggplot(aes(y=SSB,x=Year,label=Year,color=Assessed_Year)) +
   geom_line(stat='Identity',width=2) + theme_minimal() +
   facet_wrap(stock~region,scale="free") + expand_limits(y = 0)
```

```{r,echo=FALSE,warning=FALSE,fig.width=11,fig.height=18}
df<-tibble(left_join(mod_stats,sara_stock));
names(df) <- tolower(names(df))
df |> filter(assessyear==2021) |> ggplot(aes(x=spawnbiomass,y=recruitment,label=fisheryyear)) + 
  geom_point(size=.2) + geom_smooth() + theme_minimal() + facet_wrap(stock~region,scale="free")
```

